---
title: "Volume Analysis"
author: "Min Zhang"
output: 
  html_document: 
    toc: true
    toc_float: true
    df_print: paged
    code_float: hide
    code_folding: hide    #hide code to dropdown
    theme: flatly
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(output = FALSE)

#install.packages("rstatix")
library(stringr)
library(dplyr)
library(tidyverse)
library(readxl)
library(ggplot2)
library(ggcorrplot)
library(tidyr)
library(dplyr)
library(data.table)
#library(ggpubr)
library(psych)
library(rstatix)

# read in data
#source("~/Dropbox (University of Oregon)/EmoReg_CamCAN/AnalysisMZ/VolumeanalysisDFMZ.R")
Volume <- read_csv("~/EmoReg_CamCAN/camcan_ER_with_ROI_volume.csv")
#Data summary for error bar 
#+++++++++++++++++++++++++
# Function to calculate the mean and the standard deviation
  # for each group
#+++++++++++++++++++++++++
# data : a data frame
# varname : the name of a column containing the variable
  #to be summariezed
# groupnames : vector of column names to be used as
  # grouping variables
Data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE))
  }
  data_sum <- ddply(data, groupnames, .fun=summary_func, varname)
  data_sum <- rename(data_sum, c("mean" = varname))
  return(data_sum)
}

```

```{css document style, echo=FALSE}
<!-- p { -->
<!--   font-size: 12px; -->
<!-- } -->
<!-- h1, h2, h3 { -->
<!--   text-align: center; -->
<!-- } -->
```
# DESCRIPTION OF EXPERIMENT 
=========================
Subjects view 30 second film clips across four different conditions: Watch Neutral, Watch Positive, 
Watch Negative and Reappraise Negative. In the watch conditions they are instucted to simply watch
the films and allow for their emotions to arise naturally. In the reappraise condition they are 
asked to reduce their negative emotions by changing the way they think about the content of the films.
After each film clip they are instructed to rate their emotions during the film. Ratings are provided 
on two likert scales measuring positive and negative emotions, ranging from '0' = Not Negative/Positive
at all to '100' = Extremely Negative/Positive.
After their mood ratings participants are asked how well they were able to complie with the task
instuction by indicating on a Likert scale how much they Reappraised/Watch the film clip.

Ratings on all scales are made by moving a cursor up and down the scales using the left and right arrow
keys.

The task is implemented in E-Prime 2. 


#  Variable  

VARIABLE               DESCRIPTION                      		                     UNITS/RANGE
----------------      ------------------------------   		                       ---------------
CCID                  CamCAN ID (string)                                          CC######
Ntrials               Number of trials                                            Integer (0:38)
PctExpectted          Percent of # expected trials                                Ntrials/38
Version               Version of experiment                                       1|2|3|4
NeuW_neg              Negative emotion rating for Watch Neutral                   1-11
NeuW_pos              Positive emotion rating for Watch Neutral                   1-11
NeuW_WvsR             Instruction adherence rating for Watch Neutral              1-11
NeuW_aver	
NegW_neg              Negative emotion rating for Watch Negative                  1-11
NegW_pos              Positive emotion rating for Watch Negative                  1-11
NegW_WvsR             Instruction adherence rating for Watch Negative             1-11
NegW_aver	
PosW_neg              Negative emotion rating for Watch Positive                  1-11
PosW_pos              Positive emotion rating for Watch Positive                  1-11
PosW_WvsR             Instruction adherence rating for Watch Positive             1-11
PosW_aver	
NegR_neg              Negative emotion rating for Reappraise Negative             1-11
NegR_pos              Positive emotion rating for Reappraise Negative             1-11
NegR_WvsR             Instruction adherence rating for Reappraise Negtive         1-11
NegR_aver
Pos_Reactivity        Positive watch (pos scale) - Negative watch (pos scale)     1-11
Neg_Reactivity        Negative watch (neg scale) - Positive watch (neg scale)     1 -11
Pos_Reactivity_Neutral      Positive watch (pos scale) - Neutral watch (pos scale)     1-11
Neg_Reactivity_Neutral      Negative watch (neg scale) - Neutral watch (neg scale)     1 -11
Pos_scale_reappraisal Negative Reappraise (pos scale) - Negaitve Watch pos scale) 1-11
Neg_scale_reappraisal Negative Reappraisal (neg scale) - Negative Watch (neg scale) 1-11


Subjective Emotion Regulation: was created to capture tp what degree subjects felt they were following the reappraise instruction)

Sub_Regulation = NegR_WvsR – NegW_WvsR


<br>

(Emotion Regulation Success)

Pos_Reg_Success = NegR_pos – NegW_pos

Neg_Reg_Success = NegW_neg - NegR_neg

Reg_Success = Average (Pos_Reg_Success & Neg_Reg_Success)


<br> 

(Emotion Reactivity):comparing the ratings during the positive and negative films

Pos_recativity = PosW_pos – NegW_pos 

Neg_recativity = NegW_neg – PosW_neg

Reactivity = average (Pos_recativity & Neg_Reactivity) 


Reactivity (compare to neutral watch):comparing the ratings during the positive and negative films to those from the neutral films

Pos_Reactivity_Neutral = PosW_pos - NeuW_pos
Neg_Reactivity_Neutral = NegW_neg - NeuW_neg
Reactivity_Neutral = (Pos_Reactivity + Neg_Reactivity) /2   # Mean


<br> 



# Checking Data
Volume 571 participants (# no data for 135, 398, 515,547, 558)
262 participants in behavior data 
398, 515 are in the csv file that used for old analysis, but no data in stats folder so they are not included.

259 participants was in the final analysis

Hipp_L, Hipp_R, AMYG_L, AMYG_R are highly correlated, so decide use AMY mean for anylasis mean(left_Amygdala, right_Amygadala)

```{r reset data type, echo = FALSE, message=FALSE}
Volume$age_group <- as.factor(Volume$age_group)
```

## Correlation b/t brain region
```{r Correlation b/t brain region, collapse = TRUE}
# Correlation b/t brain region 
Brain_cor <- Volume %>%
  select(left_Hippocampus, right_Hippocampus, left_Amygdala, right_Amygdala)%>%
  cor(method = "pearson") 
  
# P-Value
Brain_cor_p_value <- Volume %>%
  select(left_Hippocampus, right_Hippocampus, left_Amygdala, right_Amygdala)%>%
  cor_pmat(method = "pearson")
print(Brain_cor)
#Brain_cor_plot
ggcorrplot(Brain_cor, colors = c("#B0CFFB", "white", "#31507A")) +
  labs(title = "Brain Region Correlation")

#Gender and brain correlation
genderSum <- Volume %>%
  group_by(gender_text, age_group)%>%
  summarise(mean = mean(Amygdala),
            sd = sd(Amygdala),
            n = n())%>%
  mutate(se=sd/sqrt(n)) %>%
  mutate(ic=se*qt((1-0.5)/2+.5, n-1))
  
ggplot(genderSum, aes(x=age_group, y=mean, fill=gender_text))+
  geom_bar(stat="identity", position = position_dodge())+
  scale_fill_brewer((palette="gender"))+
  labs(x = "Age Group", y = "Mean of Amygdala",title = "Gender and Amygdala")+
  geom_errorbar(aes(ymin=mean-se, ymax = mean+se), width=.2, position = position_dodge(.9))+  scale_x_discrete(labels = c("18-30", "31-59", ">60"))

AMY <- Volume$Amygdala
Hipp <- Volume$Hippocampus
t.test(Volume$Amygdala,Volume$gender_code)

boxplot(Amygdala ~ gender_text, data = Volume)

# Correlation:Amygdala ~ age 
cor(Volume$age, Volume$Amygdala)
lmAge_AMY <- lm(Amygdala ~ age, Volume)
summary(lmAge_AMY)
ggplot(Volume, aes(x = age , y = Amygdala))+
  geom_point(color = "#31507A") +
  geom_smooth(method = "lm") 
#Correlation on age and Hippocampus
cor(Volume$age, Volume$Hippocampus)
ggplot(Volume, aes(x = age, y = Hippocampus))+
  geom_point(color = "#31507A") +
  geom_smooth(method = "lm") +
  labs(x="age", y="Hippocampus")
```


```{r normality check, message=FALSE,include=FALSE, collapse = TRUE}
# normality
hist(Volume$Sub_Regulation)
hist(Volume$Amygdala)
mean(Volume$Amygdala)

### Amygdala 
AMY <- Volume %>%
  group_by(age_group)%>%
  summarise(MeanAMY = mean(Amygdala,na.rm = T))
Volume$AMYSizeGroup[Volume$Amygdala > 1604] <- "large"
Volume$AMYSizeGroup[Volume$Amygdala < 1604] <- "small"
#Volume$AMYSizeGroup <- factor(Volume$AMYSizeGroup, 
#                                 levels = c("1", "2"),
#                                 labels = c("Smaller", " Larger"))

ggplot(Volume, aes(x = Reg_Success , y = AMYSizeGroup))+
  geom_point(color = "#31507A") +
  geom_smooth(method = "lm")+
  labs(x="Emotion Regulation Success", y="age")
#This interval is defined so that there is a specified probability that a value lies within it. It is calculated as t * SE. Where t is the value of the Student???s t-distribution for a specific alpha. Its value is often rounded to 1.96 (its value with a big sample size). If the sample size is huge or the distribution not normal, it is better to calculate the CI using the bootstrap method, however.

#alpha=0.05
#t=qt((1-alpha)/2 + .5, length(vec)-1)   # tend to 1.96 if sample size is big enough
#CI=t*se
sum <- Volume %>% 
  group_by(age_group, AMYSizeGroup) %>% 
  summarise(n=n(),
            mean=mean(Sub_Regulation),
            sd=sd(Sub_Regulation))%>%
  mutate(se=sd/sqrt(n)) %>%
  mutate(ic=se*qt((1-0.5)/2+.5, n-1))
sum <- Volume %>% 
  group_by(age_group) %>% 
  summarise(n=n())
#describe.by(Volume, Volume$age_group, mat = T)
#Volume_sum <- Data_summary(Volume, "Reg_Success", c("age_group", "AMYSizeGroup"))
# error with standard Error y = Sub_Regulation Mean
# ggplot(sum, aes(x=age_group, y=mean, fill=AMYSizeGroup))+
#   geom_bar(stat="identity", position = position_dodge())+
#   scale_fill_brewer((palette="AMY Size Group"))+
#   labs(x = "Age Group", y = "Mean of Sub_Regulation")+
#   geom_errorbar(aes(ymin=mean-se, ymax = mean+se), width=.2, position = position_dodge(.9))+  scale_x_discrete(labels = c("18-30", "31-59", ">60"))
#   
# 
# #ggboxplot(Volume, x="age_group", y = "Sub_Regulation", color = "AMYSizeGroup")+
#  # scale_x_discrete(labels = c("18-30", "31-59", ">60"))
# #
# ggplot(Volume, aes(x = age, y = Sub_Regulation, group = AMYSizeGroup, color = AMYSizeGroup))+
#   geom_point()+
#   geom_smooth(method = "lm")+
#   scale_color_manual(name = "AMYSizeGroupp",
#                      breaks = c("small", "large"),
#                      labels = c("Smaller", "Larger"),
#                      values = c("#E6B39A","#8EBEE6","#998B50"))+
#   labs(x="age", y="Emotion Regulation Success")

```

### Regulation abilities by age 
```{r trying to do mutiple anova, include=FALSE, collapse = TRUE}
Ratingdf <- pivot_longer(Volume, c(PosW_neg,NeuW_neg,NegW_neg,NegR_neg), names_to = "Condition", values_to = "Rating")
#  select(c(ssid,age,age_group, Condition, Rating))

#NeuW_neg, NeuW_pos, NeuW_WvsR, NegW_neg, NegW_pos, NegW_WvsR, PosW_neg,
 #                                PosW_pos, PosW_WvsR, NegR_neg, NegR_pos, NegR_WvsR, Pos_Reactivity,
  #                               Neg_Reactivity, Reactivity, Sub_Regulation, Pos_Reg_Success, Neg_Reg_Success, Reg_Success
pairwise.t.test(Ratingdf$Rating, Ratingdf$Condition, p.adjust.method = "none",paired = T)
Rating_Ano <-  aov(Rating~Condition+Error(ssid),data = Ratingdf)
A<-summary(Rating_Ano)
#R<-TukeyHSD(A)
Ratingdf_agg <- Ratingdf %>%
  group_by(Condition,ssid) %>%
  summarise(Neg_Rating = mean(Ratingdf$Rating),n =n())
#Volume %>% anova_test(dv=Rating, wid=ssid, within = c(PosW_neg, NegW_neg, NeuW_neg, NegR_neg))
ggplot(Ratingdf_agg, aes(x= Condition, y = Neg_Rating))+
  geom_point()+
  geom_smooth(method = "lm")

hist(Volume$PosW_neg)
hist(Volume$PosW_pos)
hist(Volume$NeuW_WvsR)


abilities<- Volume %>%
  group_by()

```



# Linear regression {#linear-regression}

## Subjective Emotion Regulation
```{r Sub_Regulation, message=FALSE, include=FALSE}
#lm(target variable (Dependent variable) ~ predictor variables (independent variable), data = data source)
```

### age/Amygdala~Sub_Regulation
```{r age~Sub_Regulation, message=FALSE, collapse = TRUE}
#Linear regression on age and sub_regulation
lmSub_reg_Age <- lm(Sub_Regulation~age, Volume)
summary(lmSub_reg_Age)
ggplot(Volume, aes(x = age, y = Sub_Regulation))+
  geom_point(color = "#31507A")+
  geom_smooth(method = "lm")+
  labs(x="Age", y = "Subjective Emotion Regulation")+
  labs(title = "Age and Subjective Emotion Regulation")

#sub_Regulation ~ Amygdala ###
lmSub_reg_AMY <- lm( Sub_Regulation~Amygdala, Volume)
summary(lmSub_reg_AMY)
ggplot(Volume, aes(x = Amygdala, y = Sub_Regulation))+
  geom_point(color = "#31507A") +
  geom_smooth(method = "lm")+
  labs(x="Amygdala", y = "Subjective Emotion Regulation") +
  labs(title = "Amygdala and Subjective Emotion Regulation")

# Sub_Regulation ~age + Amygdala ###
lmSub_reg_Age_AMY <- lm(Sub_Regulation ~ (age + Amygdala), Volume)
summary(lmSub_reg_Age_AMY)
print("age+Amygdala ~ Sub_Regulation with interaction" )
lmSub_reg_Age_AMY <- lm(Sub_Regulation ~ (age * Amygdala), Volume)
summary(lmSub_reg_Age_AMY)
ggplot(Volume, aes(x = Amygdala, y = Sub_Regulation, group = age_group, color = age_group))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual(name = "age group",
                     breaks = c("1", "2", "3"),
                     labels = c("18-30", "31-59", ">60"),
                     values = c("#E6B39A","#8EBEE6","#998B50"))+
  labs(x="Amygdala", y = "Subjective Emotion Regulation")+
  labs(title = "Amygdala and Subjective Emotion Regulation with Age group")
```


### Hippocampus ~ Sub_Regulation
```{r Hippocampus ~ Sub_Regulation, message=FALSE, collapse = TRUE}
##sub_Regulation ~ Hippocampus ###
lmSub_reg_Hipp <- lm(Sub_Regulation~Hippocampus, Volume)
summary(lmSub_reg_Hipp)
ggplot(Volume, aes(x = Hippocampus, y = Sub_Regulation))+
  geom_point(color = "#31507A") +
  geom_smooth(method = "lm")+
  labs(x="Hippocampus", y = "Subjective Emotion Regulation")+
  labs(title = "Hippocampus and Subjective Emotion Regulation")

#Sub_Regulation  age + Hippocampus###
lmSub_reg_Age_Hipp <- lm(Sub_Regulation ~ (age + Hippocampus), Volume)
summary(lmSub_reg_Age_Hipp)
print("age+Hippocampus ~ Sub_Regulation with interaction" )
lmSub_reg_Age_Hipp <- lm(Sub_Regulation ~ (age * Hippocampus), Volume)
summary(lmSub_reg_Age_Hipp)
ggplot(Volume, aes(x = Hippocampus, y = Sub_Regulation, group = age_group, color = age_group))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual(name = "age group",
                     breaks = c("1", "2", "3"),
                     labels = c("18-30", "31-59", ">60"),
                     values = c("#E6B39A","#8EBEE6","#998B50"))+
  labs(x="Hippocampus", y = "Subjective Emotion Regulation")+
  labs(title = "Hippocampus and Subjective Emotion Regulation with Age group")

```


## Emotion Regulation Success
### age/Amygdala~Reg_Success()
```{r age~Reg_Success, message=FALSE, collapse = TRUE}
### Reg_Success ~ age ###
lmReg_Succ_Age <- lm(Reg_Success~age, Volume)
summary(lmReg_Succ_Age)
ggplot(Volume, aes(x = age, y = Reg_Success))+
  geom_point(color = "#31507A")+
  geom_smooth(method = "lm")+
  labs(x="age", y = "Emotion Regulation Success") +
  labs(title = "Age and Emotion Regulation Success")

#Reg_Success ~ Amygdala ###
lmReg_Succ_AMY <- lm( Reg_Success~Amygdala, Volume)
summary(lmReg_Succ_AMY)
ggplot(Volume, aes(x = Amygdala, y = Reg_Success))+
  geom_point(color = "#31507A") +
  geom_smooth(method = "lm") +
  labs(x="Amygdala", y = "Emotion Regulation Success")+
  labs(title = "Amygdala and Emotion Regulation Success")

#Reg_Success ~ age + Amygala###
lmReg_Succ_Age_AMY <- lm(Reg_Success ~ (age + Amygdala), Volume)
summary(lmReg_Succ_Age_AMY)
print("age+Amygdala ~ Reg_Success with interaction" )
lmReg_Succ_Age_AMY <- lm(Reg_Success ~ (age * Amygdala), Volume)
summary(lmReg_Succ_Age_AMY)
ggplot(Volume, aes(x = Amygdala, y = Reg_Success, group = age_group, color = age_group))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual(name = "age group",
                     breaks = c("1", "2", "3"),
                     labels = c("18-30", "31-59", ">60"),
                     values = c("#E6B39A","#8EBEE6","#998B50"))+
  labs(x="Amygdala", y = "Emotion Regulation Success")+
  labs(title = "Amygdala and Emotion Regulation Success with age group")
```


###HIPP ~ Reg_Success
```{r Hippocampus ~ Reg_Success, message=FALSE, collapse = TRUE}
##Hippocampus ~ Reg_Success###
lmReg_Succ_Hipp <- lm(Reg_Success ~ Hippocampus, Volume)
summary(lmReg_Succ_Hipp)
ggplot(Volume, aes(x = Hippocampus, y = Reg_Success))+
  geom_point(color = "#31507A") +
  geom_smooth(method = "lm") +
  labs(x="Hippocampus", y = "Emotion Regulation Success")+
  labs(title = "Hippocampus and Emotion Regulation Success")

# Reg_Success ~age + Hippocampus###
lmReg_Succ_Age_Hipp <- lm(Reg_Success ~ (age + Hippocampus), Volume)
summary(lmReg_Succ_Age_Hipp)
print("age+Hippocampus ~ Reg_Success with interaction" )
lmReg_Succ_Age_Hipp <- lm(Reg_Success ~ (age * Hippocampus), Volume)
summary(lmReg_Succ_Age_Hipp)
ggplot(Volume, aes(x = Hippocampus, y = Reg_Success, group = age_group, color = age_group))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual(name = "age group",
                     breaks = c("1", "2", "3"),
                     labels = c("18-30", "31-59", ">60"),
                     values = c("#E6B39A","#8EBEE6","#998B50"))+
  labs(x="Hippocampus", y = "Emotion Regulation Success")+
  labs(title = "Hippocampus and Emotion Regulation Success with age group")

```

## Emotion Reactivity 
### age/Amygdala~Reactivity (Emotion Reactivity) 
```{r age~Reactivity, message=FALSE, collapse = TRUE}
### Reactivity ~ age ###
cor(Volume$age, Volume$Reactivity)
lmReactivity_Age <- lm(Reactivity ~ age, Volume)
summary(lmReactivity_Age)
ggplot(Volume, aes(x = age, y = Reactivity))+
  geom_point(color = "#31507A")+
  geom_smooth(method = "lm")+
  labs(x="Age", y = "Emotion Reactivity")+
  labs(title = "age and Emotion Reactivity")

#Reactivity ~ amygdala ###
lmReactivity_AMY <- lm(Reactivity ~ Amygdala, Volume)
summary(lmReactivity_AMY)
ggplot(Volume, aes(x = Amygdala, y = Reactivity))+
  geom_point(color = "#31507A") +
  geom_smooth(method = "lm") +
  labs(x="Amygdala", y = "Emotion Reactivity") +
  labs(title = "Amygdala and Emotion Reactivity")

#Reactivity ~ age + Amygala###
lmReactivity_Age_AMY <- lm( Reactivity ~ (age + Amygdala), Volume)
summary(lmReactivity_Age_AMY)
print("age+Amygdala ~ Reactivity with interaction" )
lmReactivity_Age_AMY <- lm( Reactivity ~ (age * Amygdala), Volume)
summary(lmReactivity_Age_AMY)
ggplot(Volume, aes(x = Amygdala, y = Reactivity, group = age_group, color = age_group))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual(name = "age group",
                     breaks = c("1", "2", "3"),
                     labels = c("18-30", "31-59", ">60"),
                     values = c("#E6B39A","#8EBEE6","#998B50"))+
  labs(x="Amygdala", y = "Emotion Reactivity")+
  labs(title = "Amygdala and Emotion Reactivity with age group")
```

### HIPP ~ Reactivity
```{r Hippocampus ~ Reactivity, message=FALSE, collapse = TRUE}
##Reactivity ~ Hippocampus ###
lmReactivity_Hipp <- lm(Reactivity ~ Hippocampus, Volume)
summary(lmReactivity_Hipp)
ggplot(Volume, aes(x = Hippocampus, y = Reactivity))+
  geom_point(color = "#31507A") +
  geom_smooth(method = "lm") +
  labs(x="Hippocampus", y = "Emotion Reactivity")+
  labs(title = "Hippocampus and Emotion Reactivity")

# Reactivity ~age + Hippocampus###
lmReactivity_Age_Hipp <- lm(Reactivity ~ (age + Hippocampus), Volume)
summary(lmReactivity_Age_Hipp)
print("age+Hippocampus ~ Reactivity with interaction" )
lmReactivity_Age_Hipp <- lm(Reactivity ~ (age * Hippocampus), Volume)
summary(lmReactivity_Age_Hipp)
ggplot(Volume, aes(x = Hippocampus, y = Reactivity, group = age_group, color = age_group))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual(name = "age group",
                     breaks = c("1", "2", "3"),
                     labels = c("18-30", "31-59", ">60"),
                     values = c("#E6B39A","#8EBEE6","#998B50"))+
  labs(x="Hippocampus", y = "Emotion Reactivity")+
  labs(title = "Hippocampus and Emotion Reactivity with age griyo")
```



## Emotion Reactivity (Neutrul) 
### age/Amygdala~Reactivity_Neutral (Emotion Reactivity Neutrul) 
```{r age~Reactivity_Neutral, message=FALSE, collapse = TRUE}
### Reactivity_Neutral ~ age ###
cor(Volume$age, Volume$Reactivity_Neutral)
lmReactivity_Neutral_Age <- lm(Reactivity_Neutral ~ age, Volume)
summary(lmReactivity_Neutral_Age)

ggplot(Volume, aes(x = age, y = Reactivity_Neutral))+
  geom_point(color = "#31507A")+
  geom_smooth(method = "lm")+
  labs(x="Age", y = "Emotion Reactivity") +
  labs(title = "Age and Emotion Reactivity (Neutrul)")

#Reactivity_Neutral ~ amygdala ###
lmReactivity_Neutral_AMY <- lm(Reactivity_Neutral ~ Amygdala, Volume)
summary(lmReactivity_Neutral_AMY)
ggplot(Volume, aes(x = Amygdala, y = Reactivity_Neutral))+
  geom_point(color = "#31507A") +
  geom_smooth(method = "lm") +
  labs(x="Amygdala", y = "Emotion Reactivity") +
  labs(title = "Amygdala and Emotion Reactivity (Neutrul)")

#Reactivity_Neutral ~ age + Amygala###
lmReactivity_Neutral_Age_AMY <- lm( Reactivity_Neutral ~ (age + Amygdala), Volume)
summary(lmReactivity_Neutral_Age_AMY)
print("age+Amygdala ~ Reactivity_Neutral with interaction" )
lmReactivity_Neutral_Age_AMY <- lm( Reactivity_Neutral ~ (age * Amygdala), Volume)
summary(lmReactivity_Neutral_Age_AMY)
ggplot(Volume, aes(x = Amygdala, y = Reactivity_Neutral, group = age_group, color = age_group))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual(name = "age group",
                     breaks = c("1", "2", "3"),
                     labels = c("18-30", "31-59", ">60"),
                     values = c("#E6B39A","#8EBEE6","#998B50"))+
  labs(x="Amygdala", y = "Emotion Reactivity")+
  labs(title = "Amygdala and Emotion Reactivity (Neutrul) with age group")

```

### HIPP ~ Reactivity_Neutral
```{r Hippocampus ~ Reactivity_Neutral, message=FALSE, collapse = TRUE}
##Reactivity_Neutral ~ Hippocampus ###
lmReactivity_Neutral_Hipp <- lm(Reactivity_Neutral ~ Hippocampus, Volume)
summary(lmReactivity_Neutral_Hipp)
ggplot(Volume, aes(x = Hippocampus, y = Reactivity_Neutral))+
  geom_point(color = "#31507A") +
  geom_smooth(method = "lm") +
  labs(x="Hippocampus", y = "Emotion Reactivity_Neutral") +
  labs(title = "Hippocampus and Emotion Reactivity (Neutrul)")

# Reactivity_Neutral ~age + Hippocampus###
lmReactivity_Neutral_Age_Hipp <- lm(Reactivity_Neutral ~ (age + Hippocampus), Volume)
summary(lmReactivity_Neutral_Age_Hipp)
print("age+Hippocampus ~ Reactivity_Neutral with interaction" )
lmReactivity_Neutral_Age_Hipp <- lm(Reactivity_Neutral ~ (age * Hippocampus), Volume)
summary(lmReactivity_Neutral_Age_Hipp)
ggplot(Volume, aes(x = Hippocampus, y = Reactivity, group = age_group, color = age_group))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual(name = "age group",
                     breaks = c("1", "2", "3"),
                     labels = c("18-30", "31-59", ">60"),
                     values = c("#E6B39A","#8EBEE6","#998B50"))+
  labs(x="Hippocampus", y = "Emotion Reactivity")+
  labs(title = "Hippocampus and Emotion Reactivity (Neutrul) with age group")

```

## Gender 
```{r Gender Effect, message=FALSE}
# Subjective Emotion Regulation ####
ggplot(Volume, aes(x = Amygdala, y = Sub_Regulation, group = gender_text, color = gender_text))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual(name = "Gender",
                     breaks = c("MALE", "FEMALE"),
                     labels = c("Male", "Female"),
                     values = c("#E6B39A","#998B50"))+
  labs(x="Amygdala", y = "Subjective Emotion Regulation")+
  labs(title = "Amygdala and Subjective Emotion Regulation with gender group")

lmSub_reg_gender_AMY <- lm(Sub_Regulation ~ gender_code, Volume)
summary(lmSub_reg_gender_AMY)

lmSub_reg_gender_AMY <- lm(Sub_Regulation ~ (Amygdala + gender_code), Volume)
summary(lmSub_reg_gender_AMY)
lmSub_reg_gender_AMY <- lm(Sub_Regulation ~ (Amygdala * gender_code), Volume)
summary(lmSub_reg_gender_AMY)

lmSub_gender_Age_AMY <- lm(Sub_Regulation ~ (age + Amygdala + gender_code), Volume)
summary(lmSub_gender_Age_AMY)
lmSub_gender_Age_AMY_int <- lm(Sub_Regulation ~ (age * Amygdala *gender_code), Volume)
summary(lmSub_gender_Age_AMY_int)



# Emotion Regulation Success ####
ggplot(Volume, aes(x = Amygdala, y = Reg_Success, group = gender_text, color = gender_text))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual(name = "Gender",
                     breaks = c("MALE", "FEMALE"),
                     labels = c("Male", "Female"),
                     values = c("#E6B39A","#998B50"))+
  labs(x="Amygdala", y = "Regulation Success")+
  labs(title = "Amygdala and Regulation Success")

lmReg_Success_gender_AMY <- lm(Reg_Success ~ gender_code, Volume)
summary(lmReg_Success_gender_AMY)

lmReg_Success_gender_AMY <- lm(Reg_Success ~ (Amygdala + gender_code), Volume)
summary(lmReg_Success_gender_AMY)
lmReg_Success_gender_AMY_int <- lm(Reg_Success ~ (Amygdala * gender_code), Volume)
summary(lmReg_Success_gender_AMY_int)

lmReg_Success_gender_AMY <- lm(Reg_Success ~ (age + Amygdala + gender_code), Volume)
summary(lmReg_Success_gender_AMY)
lmReg_Success_Age_AMY_int <- lm(Reg_Success ~ (age * Amygdala *gender_code), Volume)
summary(lmReg_Success_Age_AMY_int)


# Reactivity_Neutral ####
ggplot(Volume, aes(x = Amygdala, y = Reactivity_Neutral, group = gender_text, color = gender_text))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual(name = "Gender",
                     breaks = c("MALE", "FEMALE"),
                     labels = c("Male", "Female"),
                     values = c("#E6B39A","#998B50"))+
  labs(x="Amygdala", y = "Reactivity_Neutral")+
  labs(title = "Amygdala and Reactivity_Neutral")
lmRec_gender_AMY <- lm(Reactivity_Neutral ~ gender_code, Volume)
summary(lmRec_gender_AMY)

lmRec_gender_AMY <- lm(Reactivity_Neutral ~ (Amygdala + gender_code), Volume)
summary(lmRec_gender_AMY)
lmRec_gender_AMY_int <- lm(Reactivity_Neutral ~ (Amygdala * gender_code), Volume)
summary(lmRec_gender_AMY_int)

lmRec_gender_AMY <- lm(Reactivity_Neutral ~ (age + Amygdala + gender_code), Volume)
summary(lmRec_gender_AMY)
lmRec_gender_AMY_int <- lm(Reactivity_Neutral ~ (age * Amygdala *gender_code), Volume)
summary(lmRec_gender_AMY_int)


```

















